mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-29 Draft3.Rmd
custom functions

op2 <- list(
  dbinom=quote(dbinom(k, N, pi)),
  pbinom=quote(pbinom(k, N, pi)),
  qbinom=quote(qbinom(p, N, pi)),
  dnorm=quote(dnorm(x)),
  dnorm=quote(dnorm(x, mu, sigma)),
  pnorm=quote(pnorm(x)),
  pnorm=quote(pnorm(x, mu, sigma)),
  qnorm=quote(qnorm(alpha/2L)),
  pchisq=quote(1-pchisq(x, df)),
  qchisq=quote(qchisq(1L-alpha, df)),
  pt=quote(pt(t, N-1L)),
  qt=quote(qt(alpha/2L, N-1L)))
m2 <- lapply(op2, FUN=mathout, flags=list(cat=FALSE))

@@

For self-written functions, matters are a bit more complicated because the
underlying R package `rolog` [@rolog] cannot easily access the function name,
hence a default is chosen. The function name can be given as an attribute.

```{r, results='asis'}
f <- function(x)
{
  if(x == 0L) return(0L);
  if(x < 0L) return(-1L);
  if(x > 0L) return(1L)
}

attributes(f)$name = quote(sgn)
mathout(f)
```

>>>>

op2 <- list(
  dbinom=quote(dbinom(k, N, pi)),
  pbinom=quote(pbinom(k, N, pi)),
  qbinom=quote(qbinom(p, N, pi)),
  dnorm=quote(dnorm(x)),
  dnorm=quote(dnorm(x, mu, sigma)),
  pnorm=quote(pnorm(x)),
  pnorm=quote(pnorm(x, mu, sigma)),
  qnorm=quote(qnorm(alpha/2L)),
  pchisq=quote(1L-pchisq(x, 1L)),
  qchisq=quote(qchisq(1L-alpha, 1L)),
  pt=quote(pt(t, N-1L)),
  qt=quote(qt(alpha/2L, N-1L)))
m2 <- lapply(op2, FUN=mathout, flags=list(cat=FALSE))

@@

For self-written functions, matters are a bit more complicated. The name of a
self-written function is not transparent in R, since only the function body is
represented, as illustrated by the redefinition of `sign` below. The function is
often a nested R "call" of the form `'{'(L)`, with `L` being a list of
commands. \pkg{mathml} provides very limited support for typical control
structures.

```{r, results='asis'}
sgn <- function(x)
{
  if(x == 0L) return(0L)
  if(x < 0L) return(-1L)
  if(x > 0L) return(1L)
}

term <- quote(s <- sgn(x))
mathout(term)

hook(quote(s), quote(sg(x)))
term <- call("<-", quote(s), sgn)
mathout(term)
```

The hook (see below) is used to display \(\mathrm{sg}(x) = \{\ldots\) instead
of just \(s = \{\).
